Personalization and probabilities: impersonal propensities in online grocery shopping

### 2018-02-08 log.rmd

I went through the three reports, making many of the changes suggested. Many of these were useful and I was happy to respond to them. The main change is the overview and summary of the paper. A new paragraph towards the end of the introduction sets out the argument step by step, and the steps of the argument are also reiterated in the conclusion.

@@

     -  For reasons of word count, I wasn't able to include a detailed discussion of the Tesco user interface. Given my focus on probabilities, propensities and ordering of recommendations, I wasn't sure that was so relevant. Footnote 3 has a description of how handwritten lists and writing lists have been understood by anthropologists and literary theorists. 

@@

    - to be honest, this was a difficult report to respond to. I could sympathise with the reviewers frustration, but I think the reviewer was approaching the manuscript from a quite different episteme. I have tried to respond constructively to their difficulties, but it would require much more scaffolding to deal with them all. 

@@

    - R2 was concerned about extremely confusing methodology. I've added a sentence or two in the methodology section saying what the paper does. But I won't, I fear, be able to assuage R2's concerns. They don't countenance what I'm trying to do: ground a theoretical argument about changing modes of operational knowledge by assembling some empirical engagements -- the ethnographic event, the small experiments with Tesco APIs and recommender system models, the existing sociologies and anthropologies of shopping and lists and the archaeology of recommendation. Its not a conventional empirical research project, and the methodology of reconstruction that I use (borrowing from Dewey) does not conform to narrowly defined sociological requirements. Given the methodological pluralism of the journal, I'm hoping that this is viable. 

@@

    - it was a relief to not have to do much in responding to this report. I was happy to expand the sentences about object-oriented research.

@@

>>>>

I went through the three reports, making many of the changes suggested. Many of these were useful and I was happy to respond to them. The main change is the overview and summary of the paper. A new paragraph towards the end of the introduction sets out the argument step by step, and the steps of the argument are also reiterated in the conclusion. The main  section of the paper -- E -- now has a summary at the end, as well as various signposts along the way. Throughout these revisions, I've tried to be precise and focused about the argument of the paper: the nature of conversion events.

@@

     -  For reasons of word count, I wasn't able to include a detailed discussion of the Tesco user interface. This would be slightly tricky given web and app variations. Given my focus on probabilities, propensities and ordering of recommendations, I wasn't sure that was so relevant. Footnote 3 has a description of how handwritten lists and writing lists have been understood by anthropologists and literary theorists. 

@@

    - to be honest, this was a difficult report to fully deal with.  I could sympathise with the reviewers frustration, but I think the reviewer was approaching the manuscript from a quite different episteme. I have tried to respond constructively to their difficulties, but it would require much more scaffolding to deal with them all. 

@@

    - R2 was concerned about the confusing methodology. I've added a sentence or two in the methodology section saying what the paper does. But I won't, I fear, be able to assuage all R2's concerns. They don't countenance what I'm trying to do: ground a theoretical argument about changing modes of operational knowledge by assembling some empirical engagements -- the ethnographic event, the small experiments with Tesco APIs and recommender system models, the existing sociologies and anthropologies of shopping and lists and the archaeology of recommendation. It's not a conventional empirical research project, and the methodology of reconstruction that I use (borrowing from Dewey) does not conform to narrowly defined sociological requirements. Given the methodological pluralism of the journal, I'm hoping that this is viable. 

@@

    - it was a relief to not have to do much in responding to this report. I was happy to expand the sentences about object-oriented research as suggested in the methods section.

@@

## Thu 08 Feb 2018 11:24:54 GMT
- will do rest of Section E and conclusion today. Submit tomorrow?  
- wrote new summary for section E:

>The different encounters with the data staged in the personal relevance model cannot be reduced to any simple probabilistic calculation. Rather, as Patel's presentation of the different models, the logistics of running the models in a platform setting, the experimental validation of the model in A/B testing, and the construction of new features that sought to increase complementarities and reduce similarities suggests, the expression of propensities occurs in a changing weave of infrastructure, mathematics, history and logistics. None of these has a particularly strong relation to personhood or individual experience, even if personalization the main way this weave is figured.

- revised conclusion
